\documentclass[11pt,a4paper,twoside]{book} % Use the UniMelb Dissertation Template
\usepackage{../manuscript/style/uomthesis}
% User defined commands
\input{../manuscript/user-defined}
% User defined commands
%\usepackage{quotation}


\usepackage{xspace}
% My glossary
\input{../manuscript/glossary}
\graphicspath{{./gfx/}{../figures/}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter[Simple Responses]{Creating the Cochlear Nucleus stellate-cell network from experimental data}
\label{sec:SimpleResponsesChapter}
% \begin{synopsis}
%   Modelling large biophysically-based neural network models is
% 	 complicated by the large parameter space, various sources of
% 	 experimental data and the existence of stochasticity in
% 	 neural networks.
%\end{synopsis}




\input{Intro.tex}
\newpage
\input{GolgiRateLevel.tex}
\newpage
\input{DSRecovery.tex}
\newpage
\input{TV_Notch.tex}
\newpage
% \input{Tstellate.tex}
\newpage



\section{Discussion}

\marginpar{Discuss the relevance of creating the CN stellate model,
  especially the methods.}  The T-stellate cell microcircuit in the
cochlear nucleus is one of the most interesting neural features of the
auditory system.  It enables a high-fidelity sensory input to be
passed to higher order centres, by reproducing the spectrum in a
robust fashion \citep{BlackburnSachs:1990,May:2003} and
synchronisation to significant periodic frequencies
\citep{KeilsonRichardsEtAl:1997}.


\medskip{} 

\marginpar{Discuss the Golgi cell optimisation.  Is the filter-based
  approach effective at meeting the goal of simulating data from
  \citet{GhoshalKim:1997}?}  The Golgi cell model optimised in section
\ref{sec:golgi-cell-model} reproduces the experimental data of a
single unit in the marginal shell of the VCN \citep{GhoshalKim:1997}.

\medskip{}

Discuss the DS cell model optimisation.  What were the reasons for
using cell-based parameters, and why is this necessary?  Why aren't
the spread of ANF inputs to DS cells optimised based on your methods?
How does the optimisation routine replicate DS responses to other
stimuli, when there are already plenty?

\medskip{}

Discuss the TV cell optimisation. Is the goal of replicating wide-band
inhibition offset necessary, or is rate ratio between TS/DS/TV the
most important?  Mammalian studies show that the TV cells receive
input from TS cells, but not in rats


\section{Conclusion}


In this section I developed a biophysically-realistic model of the
T-stellate microcircuit in the cochlear nucleus.

\medskip{}

The methods used in this section are a practical and realistic means
for constructing microcircuits with sensory or feature-based
topography.  I followed the neural network modeling format as
suggested by \citet{NordlieGewaltigEtAl:2009} so that other
researchers may easily reproduce this work.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{plainnat}%bmc_article} % Style BST file
 \bibliography{../manuscript/bib/MyBib}

\end{document}
